---
title: "Group Assignment : 05/26"
author: "Abner"
date: "5/26/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Teammates
 - 107205008 財政四 鄧昱辰
 - 109102057 經濟二 許亮瑜
 - 107301060 統計四 賴政霖

We will estimate the test of MSE through k-fold Cross Validation

## 1.
Import the "Advertising.csv" data set.
```{r message = FALSE, warning = FALSE}
raw_data <- read.csv('/Users/abner/Downloads/Advertising.csv')
```

## 2.
Write a function of k that estimates the test of MSE for the linear regression of sales on TV abd radio based on the k-fold cross validation 
```{r message = FALSE, warning = FALSE}
k_fold_mse <- function(k){
  set.seed(123)
  data_sample <- sample(1:nrow(raw_data), size = nrow(raw_data))
  test_mse <- c()
  for (i in 1:k){
    test_data_index <- data_sample[(((i-1)/k)*nrow(raw_data)+1):((i/k)*nrow(raw_data))]
    test_data <- raw_data[test_data_index, ]
    train_data <- raw_data[setdiff(data_sample, test_data_index),]
    model <- lm(data=train_data, formula = sales~TV+radio)
    predicted <- predict(model, newdata=test_data)
    test_mse <- append(test_mse, mean((test_data$sales-predicted)^2))
  }
  cross_validation <- mean(test_mse)
  cross_validation
}
```

## 3. 
which of k = 5, 10 and n yields the smallest test MSE estimate?
```{r message = FALSE, warning = FALSE}
k_fold_mse(5)
k_fold_mse(10)
k_fold_mse(nrow(raw_data))
```
we can know that k = n yields the smallest MSE, and MSE = 2.705851

## 4.
Does adding TV:radio to the sales regression improve prediction accuracy?
```{r message = FALSE, warning = FALSE}
k_fold_mse_interaction <- function(k){
  set.seed(123)
  data_sample <- sample(1:nrow(raw_data), size = nrow(raw_data))
  test_mse <- c()
  for (i in 1:k){
    test_data_index <- data_sample[(((i-1)/k)*nrow(raw_data)+1):((i/k)*nrow(raw_data))]
    test_data <- raw_data[test_data_index,]
    train_data <- raw_data[setdiff(data_sample, test_data_index),]
    model <- lm(data=train_data, formula = sales~TV+radio+TV:radio)
    predicted <- predict(model, newdata=test_data)
    test_mse <- append(test_mse, mean((test_data$sales-predicted)^2))
  }
  cross_validation <- mean(test_mse)
  cross_validation
}
k_fold_mse_interaction(5)
k_fold_mse_interaction(10)
k_fold_mse_interaction(nrow(raw_data))
```
MSE gets smaller after adding the interaction term, and the k-fold interaction MSE(n)  = 0.9134679.