---
title: 'Group Assignment: 04/27'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Teammates:
- 107205008 財政四 鄧昱辰
- 107301060 統計四 賴政霖
- 109102057 經濟二 許亮瑜

我們將估計提高最低工資對就業的影響效果

## 2.
將 minwage.csv 讀入 R, 前面 6 筆資料如下
```{r message=FALSE, warning=FALSE}
library(tidyverse)
minwage <- read.csv(file.path("../datasets/minwage.csv"))
head(minwage)
```

## 3.
分別用 Base R 與 tidyverse 完成 3.1-3.3，所得 data frame 如下

### **Base R Version**

### 3.1
依下列定義產生 3 個新變數
```{r}
fteBefore <- minwage$fullBefore + 0.5 * minwage$partBefore
fteAfter <- minwage$fullAfter + 0.5 * minwage$partAfter
NJ <- ifelse(minwage$location == "PA", 0, 1)
```

### 3.2
將”before”與”after”同類型變數垂直堆疊成一個變數，並增加一虛擬變數“after”: after=1 indicating the “after” period
```{r}
fte <- c(fteAfter, fteBefore) 
after <- c(rep(1, 358), rep(0, 358))
```

### 3.3
保留 fte、NJ、after 三個變數
```{r}
minwage_newdata_1 <-  data.frame(fte = fte, NJ = NJ,  after = after)
head(minwage_newdata_1, 10)
```


### **Tidyverse Version**
### 3.1
```{r}
minwage_mutate <- minwage %>% 
                  mutate(fteBefore = fullBefore + 0.5*partBefore, 
                         fteAfter = fullAfter + 0.5*partAfter, 
                         NJ = ifelse(location == "PA", 0, 1))
```

### 3.2
```{r}
minwage_gather <- minwage_mutate %>% 
                  gather(key = "ftetype", value = "fte", fteAfter:fteBefore) %>%
                  mutate(after = ifelse(ftetype == "fteAfter", 1, 0))
```

### 3.3
```{r}
minwage_newdata_2 <- minwage_gather %>% select(fte, NJ, after)
head(minwage_newdata_2, 10)
```


## 4.
檢查 3.用 Base R 與 tidyverse 得到的兩個 data frames 是否完全
一樣?
```{r}
dplyr::setequal(minwage_newdata_1, minwage_newdata_2)
```

## 5.
考慮一直線迴歸模型: fte ~ NJ + after + NJ:after，請解釋此一迴
歸模型 4 個係數的經濟意義
```{r}
DID <- lm(fte ~ NJ + after + NJ:after, data = minwage_newdata_2)
summary(DID)
```

## 6.
估計 4.的迴歸模型係數並解釋結果

fte = 20.299 means if people lives in PA and before wage adjustment, 
the minimum wage = 20.299.

People in PA get 3.01 higher minimum wage than people doesn't live in PA.

The minimum wage before wage adjustment is 2.134 higher than 
the minimum wage after adjustment.(It's not significant)

If people lives in PA and after wage adjustment, the minimum wage will increase by 2.446.(Not significant too)

 |          |  NJ = 0   |   NJ = 1 |
 |----------|-----------|----------|
 |after = 0 | "20.299"  |  "17.289"|
 |after = 1 | "18.165"  |  "22.745"|
